\section{Data Acquisition and Method}

In this paper, we focus on the P-to-S converted phase to study the seismic discontinuities in the lithosphere. We apply the receiver function method \cite[e.g.][]{Langston_1979,ammon1991isolation} to extract the converted phases from the P-wave coda of teleseismic events. The receiver function method is a widely used approach, which enhances the shear-wave signal by deconvoluting the vertical component from the radial component of the seismic records. However, the deconvolution process is usually unstable due to the existence of noise in the real data. We select the time-domain iterative method to obtain the receiver function \cite{ligorria1999iterative}

is used to enhance the shear wave signal in the teleseismic P wave coda. The method 



As one of the most widely used approaches, receiver function method enhances the shear wave signal in the teleseismic P wave coda converted at subsurface discontinuities underneath the receiver. Time delay between the refracted S phase and direct P phase can be used to estimate the depth of the converting interface. 
Individual receiver function of each event-station pair can be estimated by the deconvoluting the vertical component from radial component of teleseismic P wave and its coda [Langston, 1979; Ammon, 1991]. In order to stabilize this deconvolution, the time-domain iterative deconvolution approach was adopted in this study [Ligorría and Ammon, 1999].

Since the signal to noise ratio of single receiver function trace is low because of the small P-S refraction coefficient, traces with overlapping ray path are usually stacked together to enhance the signal. Usually common conversion point (CCP) stacking is considered as the standard procedure for receiver function imaging, in which individual receiver function is applied moveout correction to zero offset, and then stacked due to the location of their piercing point at different depth. However, CCP stacking method has difficulties to reconstruct complex geometry of the refractors if lateral heterogeneity is significant or the imaged interface is dipping steeply [Ryberg and Weber, 2000]. In order to improve image quality, We adopted the pre-stack Kirchhoff migration [Wilson and Aster, 2005] to deal with the complex geometry of interfaces. In this method, the imaged space is treated as a grid of point scatters, and each receiver function is rescaled and back-projected to all the possible scattering points. A 1D reference model with 75km crustal thickness is used for ray tracing and converting the delay time into depth. After the summation of all receiver functions, we normalized the amplitude of output grid for better illumination. The normalization is only applied in depth domain and each horizontal location in the profile is normalized independently. 
Besides 14 boardband stations that we operated in this region for almost one year and half, we also collected data from 1 INDEPTH II station, 9 INDEPTH III stations and 6 years data from permanent station LSA (shown as Figure 1). Receiver functions were then estimated using teleseismic events with epicenter distance from 30°to 90°, and magnitude over 5.5. After carefully visual selection, totally 1335 receiver function waveforms with high signal to noise ratio were selected from PKU stations, 27 from Indepth II stations, 88 from Indepth III stations, and 51 from Lhasa station.
